
***

This folder is created to allow us to evaluate and
compare different recommendation models (say, arising
from varying the values of certain parameters). It 
contains three sets of training-validation data (all
extracted from the original training data), and an R
script for evaluation.

***

### What files are there?

* __split1/__: a folder containing a training-validation set,
coming from the parts of the original training data in the
period from 2011-07-01 to 2012-06-16 and the period from
2012-06-17 to 2012-06-23

* __split2/__: a folder containing a training-validation set,
coming from the parts of the original training data
in the period from 2011-07-01 to 2012-06-09 and the period from
2012-06-10 to 2012-06-16

* __split3/__: a folder containing a training-validation set,
coming from the parts of the original training data
in the period from 2011-07-01 to 2012-06-02 and the period from
2012-06-03 to 2012-06-09

* __map.R__: an R script that calculates the mean average
precision (MAP) of any recommendation result

***

### How to use the files?

1. Pick a set of training-validation data (see above).

2. Run your algorithm on the training data.

3. Put your results into a data frame with the following format:
+ the first column consists of all the user IDs and is named
USER_ID_hash; 
+ the other columns are the IDs of the recommended coupons,
in descending order of confidence.

4. Load the purchase records from the validation week.
```{r, eval=FALSE}
load("coupon_purchased_test.RData")
```

5. Calculate the mean average precision (MAP) of your
recommendations.
```{r, eval=FALSE}
source("map.R")
MAP(predict, coupon_purchased_test)   # 'predict' refers to the data frame created in step 3
```

***


